Playing against Nature: causal discovery for decision making under uncertainty

### 2018-05-14 Segundo_Semestre/CausalML_Workshop/Paper_short_version.tex
mencionando los 3 casos antes de seccion 5.1
cambio redaccion en only structure is known

@@

>>>>

We consider three cases of increasing complexity:
\begin{itemize}
\item The decision maker fully knows the causal model.
\item The decision maker knows only the graph structure.
\item The decision maker knows nothing about the causal model. 
\end{itemize}

@@

\subsection{The model is not known}
The causal model were unknown, the decision maker will have to deal with the problem using only any previous knowledge and his own intuitions. The set of any previous knowledge and considerations will be known as \textit{beliefs}, which will take the form of a probability distributions over causal models.
